Fitbit & ET Glasses - Methods

### 2022-07-18 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/FitBit_ET_Glasses_Methods.Rmd
fitbit data

For the first simulation the participant was standing still without moving its head and with stong movements of the head respectively. A reliable measurement would give the same distance for both situations. 
Afterwards, we simulated two two times 5 meter long walks. One time the participant turned around after 5 meters. During the other walk the participant walked 5 meters and walked back backwards. Again, we expect the glasses to give the same walking distance.
To test real world situations we simulated two random walks in a simulated class room. One walk simulated an extensive walk and the other walk simulated a less intense walk.
Additionally, we tested the values for taking the elevator and walking a staircase.
The simulated situations give the following values.

@@

```{r}
df_steps <- read_rds(file = "final_data/steps.rds")
set.seed(5678)
ggplot(data = df_steps,
       mapping = aes(x = type,
                     y = Steps
                     )
       ) +
  geom_boxplot(mapping = aes(color = type),
               fill = "grey",
               alpha = 0.6) +
  geom_jitter(mapping = aes(color = type),
              alpha = 0.9,
              width = 0.3) + 
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  labs(x = "",
       y = "Steps During\nMain Phase") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()
        ) 
```

>>>>

For the first simulation the participant was standing still without moving its head and with strong movements of the head respectively. A reliable measurement would give the same distance for both situations. 
Afterwards, we simulated two two times 5 meter long walks. One time the participant turned around after 5 meters. During the other walk the participant walked 5 meters and walked back backwards. Again, we expect the glasses to give the same walking distance.
To test real world situations we simulated two random walks in a simulated class room. One walk simulated an extensive walk and the other walk simulated a less intense walk.
Additionally, we tested the values for taking the elevator and walking a staircase.
The simulated situations give the following values.

@@

```{r}
df_steps <- read_rds(file = "final_data/steps.rds")
set.seed(5678)
ggplot(data = df_steps,
       mapping = aes(x = type,
                     y = Steps
                     )
       ) +
  geom_boxplot(mapping = aes(color = type),
               fill = "grey",
               alpha = 0.6) +
  geom_jitter(mapping = aes(color = type),
              alpha = 0.9,
              width = 0.3) + 
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  labs(x = "",
       y = "Steps During\nMain Phase") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()
        )

### Validation of steps 
# selecting some rows at random with sample_n()
sample_n(df_steps, 6)

# Output:
# Experts: 219, 218, 214
# Novices: 108, 117, 110
